---
title: "Movers Calculation"
author: "Julie Norman"
purpose: "Create 5% sample cohort of MBSF patients including variables on county occupancy, hospitalization and demographic details"
date: "2024-07-09"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```


## Libraries

```{r include=FALSE}
library(tidyverse)
library(lubridate)
library(data.table)
library(haven)
library(mosaic)
library(microbenchmark) # calc runtime

```


```{r}
 cohraw_df <- fread('/project/Burke_PAC_MA/Analysis/Norman/Raw Data for R/SongCohort0618_0913.csv')

# cohraw_exp <- cohraw_df %>%
#   select(BENE_ID, MEDPAR_ID, PRVDR_NUM, RFRNC_YR, ADMSNDT, DSCHRGDT, DEATHDT, RTI_RACE_CD, BENE_DOB, CCI_TOT_GRP, FIPS_hosp)

names(cohraw_df) <-tolower(names(cohraw_df))

write_rds(cohraw_df, '/project/Burke_PAC_MA/Analysis/Norman/Raw Data for R/SongCohortSel0618.rds')
```

```{r}

```

## Questions

how to handle when years are limited: 
	
llllll00A0JAA0j only has 2019 Jan-sept

no multiple hospitalizations per quarter, intuitive sense?

Review final two graphics

what prop have at least 1 hosp in the year



# 5% sample quarterly movers

```{r}
mbsftst <- mbsfsamp5_df %>% 
  select(bene_id, rfrnc_yr, rfrnc_qrt) %>% 
  group_by(bene_id) %>% 
  summarise(benecnt = n())
  
```


```{r}
set.seed(8675309)

mbsf_df <- fread("/project/Burke_PAC_MA/Analysis/Norman/Raw Data for R/RawMbsfDem1519B.csv")

names(mbsf_df) <-tolower(names(mbsf_df))

patsamp5_df <- mbsf_df %>%
  select(bene_id) %>%
  distinct() %>%
  sample_frac(.05)

mbsfsamp5_df <- mbsf_df %>% 
  inner_join(patsamp5_df)

write_rds(mbsfsamp5_df, "/project/Burke_PAC_MA/Analysis/Norman/Output/Rand Sample/MBSFraw05p091824.rds")

# patsamp1_df <-  mbsfraw1_df %>% 
#   select(BENE_ID, BENE_DOB, RTI_RACE_CD) %>% 
#   distinct() 
# 
# names(patsamp1_df) <-tolower(names(patsamp1_df))

#cohraw_df <- read_rds('/project/Burke_PAC_MA/Analysis/Norman/Raw Data for R/SongCohortSel0618.rds')


```



### Calc Quarterly Movers

```{r}
mbsfsamp5_df <- read_rds("/project/Burke_PAC_MA/Analysis/Norman/Output/Rand Sample/MBSFraw05p091824.rds")

ind_repeat_pattern <- function(input_string) {
  # Function to check if the input string is made of repeating 5-character patterns
  check_repeating_pattern <- function(x) {
    n <- nchar(x)
    
    # Ensure the string length is not zero and is a multiple of 5
    if (n == 0 || n %% 5 != 0) {
      return("No")
    }
    
    # Extract the repeating unitfip_combfip_combfip_comb
    pattern_length <- 5
    pattern <- substr(x, 1, pattern_length)
    
    # Create a repeated pattern of length equal to input_string
    repeated_pattern <- paste(rep(pattern, n / pattern_length), collapse = "")
    
    # Check if the repeated pattern matches the entire string
    if (repeated_pattern == x) {
      return("Yes")
    }
    
    return("No")
  }
  # Apply the function to each element in the input vector
  sapply(input_string, check_repeating_pattern)
}
  
  
# divide movers and non movers
mbsf5_df2 <- mbsfsamp5_df %>%
  arrange(bene_id, rfrnc_yr) %>%
  #slice_head(n = 10000) %>% 
  mutate(
  fip_q1 = case_when(
    is.na(state_cnty_fips_cd_01) == FALSE ~ 
      state_cnty_fips_cd_01,
    is.na(state_cnty_fips_cd_01) == TRUE &
      is.na(state_cnty_fips_cd_02) == FALSE ~
      state_cnty_fips_cd_02,
    is.na(state_cnty_fips_cd_01) == TRUE &
      is.na(state_cnty_fips_cd_02) == TRUE &
      is.na(state_cnty_fips_cd_03) == FALSE ~
      state_cnty_fips_cd_03,
    is.na(state_cnty_fips_cd_01) == TRUE &
      is.na(state_cnty_fips_cd_02) == TRUE &
      is.na(state_cnty_fips_cd_03) == TRUE ~ NA),
   fip_q2 = case_when(
    is.na(state_cnty_fips_cd_04) == FALSE ~ 
      state_cnty_fips_cd_04,
    is.na(state_cnty_fips_cd_04) == TRUE &
      is.na(state_cnty_fips_cd_05) == FALSE ~
      state_cnty_fips_cd_05,
    is.na(state_cnty_fips_cd_04) == TRUE &
      is.na(state_cnty_fips_cd_05) == TRUE &
      is.na(state_cnty_fips_cd_06) == FALSE ~
      state_cnty_fips_cd_06,
    is.na(state_cnty_fips_cd_04) == TRUE &
      is.na(state_cnty_fips_cd_05) == TRUE &
      is.na(state_cnty_fips_cd_06) == TRUE ~ NA),
  fip_q3 = case_when(
    is.na(state_cnty_fips_cd_07) == FALSE ~ 
      state_cnty_fips_cd_07,
    is.na(state_cnty_fips_cd_07) == TRUE &
      is.na(state_cnty_fips_cd_08) == FALSE ~
      state_cnty_fips_cd_08,
    is.na(state_cnty_fips_cd_07) == TRUE &
      is.na(state_cnty_fips_cd_08) == TRUE &
      is.na(state_cnty_fips_cd_09) == FALSE ~
      state_cnty_fips_cd_09,
    is.na(state_cnty_fips_cd_07) == TRUE &
      is.na(state_cnty_fips_cd_08) == TRUE &
      is.na(state_cnty_fips_cd_09) == TRUE ~ NA),
   fip_q4 = case_when(
    is.na(state_cnty_fips_cd_10) == FALSE ~ 
      state_cnty_fips_cd_10,
    is.na(state_cnty_fips_cd_10) == TRUE &
      is.na(state_cnty_fips_cd_11) == FALSE ~
      state_cnty_fips_cd_11,
    is.na(state_cnty_fips_cd_10) == TRUE &
      is.na(state_cnty_fips_cd_11) == TRUE &
      is.na(state_cnty_fips_cd_12) == FALSE ~
      state_cnty_fips_cd_12,
    is.na(state_cnty_fips_cd_10) == TRUE &
      is.na(state_cnty_fips_cd_11) == TRUE &
      is.na(state_cnty_fips_cd_12) == TRUE ~ NA)
    ) %>% 
  select(bene_id, rfrnc_yr, starts_with("fip_q")) %>% 
   mutate(
    missfip_all = ifelse(is.na(fip_q1) == TRUE &
                           is.na(fip_q2) == TRUE &
                           is.na(fip_q3) == TRUE &
                           is.na(fip_q4) == TRUE, 1, 0),
    fip_comb = paste0( # 5 digit fip to maintain pattern of 5
      sprintf("%05d", fip_q1),   
      sprintf("%05d", fip_q2),
      sprintf("%05d", fip_q3),
      sprintf("%05d", fip_q4)
    ) %>% gsub("NA| ", "", .) # Adjusted to handle NA values at the start
  ) %>%
  filter(missfip_all == 0) %>%  # pat with all missing rows, new n = 3689915
  mutate(nonmove_yr = 
           ind_repeat_pattern(fip_comb),
         fip_frst =  substr(fip_comb, 1, 5)) %>% 
  group_by(bene_id) %>%
  mutate(frst_fip_cnt =
           n_distinct(fip_frst)) %>% 
  mutate(mover_ind = ifelse(any(nonmove_yr == "No") | any(frst_fip_cnt > 1), 1, 0)) %>% 
  ungroup() # mover_ind has no NA
# 3689915 bene

write_rds(mbsf5_df2, "/project/Burke_PAC_MA/Analysis/Norman/Output/Rand Sample/mbsf05p092724.rds")
  
# non-mover should have 3305087 unique bene_id, shouldn't/doesn't change
non_move5_df <- mbsf5_df2 %>% 
  filter(mover_ind == 0) %>% 
  mutate(move_yr = NA,
         move_qrt = NA,
         num_moves = 0,
         row_fip1 = apply(
           select(., starts_with("fip_q")), 1, min, na.rm = TRUE),
         row_fip2 = apply(
           select(., starts_with("fip_q")), 1, max, na.rm = TRUE)) %>% 
  group_by(bene_id) %>% 
  mutate(fip_chk = row_fip1 == row_fip2, # all true
         fip_strt = min(row_fip1, na.rm = TRUE),
         fip_end = max(row_fip1, na.rm = TRUE)) %>% # check for diff 
  mutate(diff_fip = ifelse(fip_strt == fip_end, FALSE, TRUE) ) %>% 
  # all false
  select(bene_id, mover_ind, num_moves, move_yr, move_qrt, fip_strt, fip_end) %>% 
  distinct()
# nrow = 3305087
# unique bene = 3305087
# mover_ind = num_moves = 0 for all
# no missing for fip_ vars

## MOVERS ##
# All mover count: 384828 ben_id
move5_df <- mbsf5_df2 %>%
  filter(mover_ind == 1 ) %>% #384828 bene
  select(bene_id, rfrnc_yr, starts_with("fip_q")) %>%
  arrange(bene_id, rfrnc_yr) %>%
  group_by(bene_id) %>%
  pivot_longer(cols = starts_with("fip_q"),
               names_to = "qrt_col", values_to = "fip") %>%
  filter(is.na(fip) == FALSE) %>%   #384828 bene
  mutate(fips_change =  fip != lag(fip) ) %>%
  group_by(bene_id) %>%
  mutate(fip_strt = first(fip, na_rm = TRUE),
         fip_end = last(fip, na_rm = TRUE),
         move_cnt_all = sum(fips_change, na.rm = TRUE)) %>% 
  filter(move_cnt_all == 1 & fips_change == TRUE) %>% 
          # multiple moves removed, 302483 bene left
  mutate(
    move_yr = (rfrnc_yr),
    move_qrt = as.numeric(str_sub(qrt_col, -1)),
    mover_ind = 1,
    num_moves = 1,
  ) %>%
  ungroup() %>%
  select(bene_id, mover_ind, num_moves, move_yr, move_qrt, fip_strt, fip_end) %>% 
  distinct()
# nrow = n_distinct(bene) = 302483  
# Quarters Distibution
#     1     2     3     4 
# 63034 74339 75182 89928
  
# 82345 patients removed as multiple movers, 2.23% of sampled patients

mover_exp5 <- rbind(non_move5_df, move5_df) %>% 
  arrange(bene_id, move_yr) %>% 
  mutate(duplicate_flag = duplicated(bene_id) | duplicated(bene_id, fromLast = TRUE)) # no duplicates

# check bene categorization

write_rds(mover_exp5, "/project/Burke_PAC_MA/Analysis/Norman/Output/Rand Sample/MovingAllQrt05p092724.rds")




```

#### Checks
```{r}
# initial 3690462, sub missing 3689915, sub multiple, 3607570

n_distinct(mover_exp5$bene_id) #3607570
nrow(mover_exp5) #3607570

table(mover_exp5$mover_ind)
#       0       1 
# 3305087    302483   
# should match n from above

table(is.na(mover_exp5$mover_ind)) # all false

colSums(is.na(mover_exp5))
# bene_id mover_ind num_moves   move_yr  move_qrt  fip_strt   fip_end 
#         0         0         0   3305087   3305087         0         0 

```
#### final bene count
```{r}
mover_exp5 <- read_rds("/project/Burke_PAC_MA/Analysis/Norman/Output/Rand Sample/MovingAllQrt05p092724.rds")

# bene to keep
sampbene5_df <- mover_exp5 %>% 
  select(bene_id) %>% 
  distinct()
```


### time base

```{r}
mbsf5_df2 <- read_rds("/project/Burke_PAC_MA/Analysis/Norman/Output/Rand Sample/mbsf05p092724.rds")

patKeep_df <- mbsf5_df2 %>% 
  inner_join(sampbene5_df) %>% # 3607570 bene
  select(bene_id, rfrnc_yr, contains("fip_q")) %>% 
  group_by(bene_id) %>%
  pivot_longer(cols = starts_with("fip_q"),
               names_to = "qrt_col", values_to = "fip") %>% 
  # nrow = 61398016
  filter(is.na(fip) == FALSE) %>% # 2319968 dropped
  mutate( rfrnc_qrt = as.numeric(str_sub(qrt_col, -1))) %>% 
  select(bene_id, rfrnc_yr, rfrnc_qrt)


```


### Calc MA/FFS Coverage

"Coverage Status by Month, F=FFS, M=MA, X=Neither, 9=Missing"


if hmo_in[i]="0" and buy_in[i]="00" then hmo_out[i]="X"; 
			else if hmo_in[i] in ("0", "4") then hmo_out[i]="F";
			else if hmo_in[i] in ("1", "C") then hmo_out[i]="M";
	end; 


```{r}
mbsfsamp5_df <- read_rds("/project/Burke_PAC_MA/Analysis/Norman/Output/Rand Sample/MBSFraw05p091824.rds")

mbsfcov_df <- mbsfsamp5_df %>% 
  inner_join(sampbene5_df)

# Loop over suffixes 01 to 12 
for (i in 1:12) {
  suffix <- sprintf("%02d", i)  # Generate "01" to "12"
  
  # column names
  hmoind_col <- paste0("hmoind", suffix)
  buyin_col <- paste0("buyin", suffix)
  cov_col <- paste0("cov_", suffix)
  
  # Create variable
  mbsfcov_df <- mbsfcov_df %>%
    mutate(!!cov_col := case_when(
      !!sym(hmoind_col) == "0" & !!sym(buyin_col) == "00" ~ "X",
      (!!sym(hmoind_col) == "0" & !!sym(buyin_col) != "00") | !!sym(hmoind_col) == "4" ~ "F",
      !!sym(hmoind_col) == "1" | !!sym(hmoind_col) == "C" ~ "M",
      TRUE ~ "9"
    ))
}



```



```{r}
mbsfcov_df2 <- mbsfcov_df %>% 
  select(-starts_with("state")) %>% 
  mutate(cov_q1 = paste0(cov_01, cov_02, cov_03),
         cov_q2 = paste0(cov_04, cov_05, cov_06),
         cov_q3 = paste0(cov_07, cov_08, cov_09),
         cov_q4 = paste0(cov_10, cov_11, cov_12)) %>% 
  select(bene_id, rfrnc_yr, contains("cov_q")) %>% 
  pivot_longer(cols = starts_with("cov_q"),
               names_to = "rfrnc_qrt_col", 
               values_to = "coverage") %>% # no NA cov value
  mutate(rfrnc_qrt = as.numeric(gsub("cov_q", "", rfrnc_qrt_col)),
         FFS_ind = ifelse(grepl("F", coverage), 1, 0),
         MA_ind = ifelse(grepl("M", coverage), 1, 0),
         miss_ind =ifelse(grepl("X", coverage), 1, 0),) %>% 
  mutate(FM_ind = ifelse(FFS_ind == MA_ind, 1, 0)) %>% 
  select(-coverage, -rfrnc_qrt_col)
# uniq bene: 3689915, match missing filter

```

quarterly coverage
     FFF      FFM      FMF      FMM      MFF 
40094105   146542     4023   155064   106583 
     MFM      MMF      MMM 
    5005   100262 19214144 
    
NA
  bene_id  rfrnc_yr rfrnc_qrt   FFS_ind    MA_ind 
        0         0         0         0         0 
 miss_ind    FM_ind 
        0         0 

```{r}


mbsfcovFilt_df <- patKeep_df %>% 
  left_join(mbsfcov_df2)

write_rds(mbsfcovFilt_df, "/project/Burke_PAC_MA/Analysis/Norman/Output/Rand Sample/MBSFcov05p092824.rds")
```
#### Checks

```{r}
colSums(is.na(mbsfcovFilt_df))
 #  bene_id  rfrnc_yr rfrnc_qrt   FFS_ind    MA_ind 
 #        0         0         0         0         0 
 # miss_ind    FM_ind 
 #        0         0

n_distinct(mbsfcovFilt_df$bene_id)
# uniq bene:  3607570, correct

```



### Calc Patient Demograpics

Race

```{r}
mbsfsamp5_df <- read_rds("/project/Burke_PAC_MA/Analysis/Norman/Output/Rand Sample/MBSFraw05p091824.rds")

  

patRace_df <- mbsfsamp5_df %>% 
  inner_join(sampbene5_df) %>% 
  select(bene_id, rti_race_cd) %>% 
 filter(!is.na(rti_race_cd)) %>%  # Remove NA values in colb
  group_by(bene_id) %>% 
  mutate( mode_count = sum(table(rti_race_cd) == max(table(rti_race_cd))),
          race = rti_race_cd[which.max(table(rti_race_cd))]) %>% 
  mutate(race_rti = ifelse(mode_count > 1, NA, race)) %>% 
  select(bene_id, race_rti) %>% 
  distinct()
```


Other

```{r}

patAll_df <- mbsfsamp5_df %>% 
  inner_join(sampbene5_df) %>% 
  select(bene_id, bene_dob, sex,death_dt) %>% 
  distinct() %>% 
  mutate(death_dt =  ifelse(death_dt == "", NA, death_dt)) %>% 
  group_by(bene_id) %>% 
  mutate(dob_ck = n_distinct(bene_dob), # count unique entries per patient
         sex_ck = n_distinct(sex),
         dth_ck = n_distinct(death_dt)) %>% 
  mutate(bene_dob = ifelse(dob_ck > 1, NA, bene_dob), # NA for differing entries
         sex = ifelse(sex_ck > 1, NA, sex),
         dth_ck = ifelse(dth_ck > 1, NA, death_dt)) %>% 
  select(bene_id, bene_dob, sex, death_dt) %>% 
  summarize(bene_dob = first(bene_dob, na_rm = TRUE), # extract unique entry
            sex = first(sex, na_rm = TRUE),
            death_dt = first(death_dt, na_rm = TRUE)) %>% 
  distinct() %>% 
  left_join(patRace_df)
#3607570

nrow(patAll_df)
#3607570

table(is.na(patAll_df$death_dt))/3607570
#      FALSE       TRUE 
# 0.03206064 0.96793936 

table(patAll_df$sex)/3607570

#         1         2 
# 0.4609757 0.5389575 

colSums(is.na(patAll_df))
 # bene_id bene_dob      sex death_dt race_rti 
 #       0     1408      241  3491909     1564

1564/3607570
# less than 1% race missing
  
```


```{r}
patAnn_df <- mbsfsamp5_df %>% 
  inner_join(sampbene5_df) %>% 
  select(bene_id, rfrnc_yr, esrd_ind) %>% 
  distinct() # no missing

patdemsamp5_df <- patAnn_df %>% 
  left_join(patAll_df)
# 3607570 bene unique

write_rds(patdemsamp5_df, "/project/Burke_PAC_MA/Analysis/Norman/Output/Rand Sample/patDemVar05p100224.rds")

```
#### checks

```{r}
tst <- patAnn_df %>% 
  mutate(uniq_id = paste0(bene_id, as.character(rfrnc_yr))) %>% 
  mutate(dup_flag = duplicated(uniq_id) | duplicated(uniq_id, fromLast = TRUE))

table(tst$dup_flag)
# no duplicates

#stats

n_distinct(patdemsamp5_df$bene_id) #3607570

table(patdemsamp5_df$rfrnc_yr)

#    2015    2016    2017    2018    2019 
# 2841018 2913954 2991117 3067026 3143317 
# 0.18995 0.19483 0.19999 0.20506 0.21016
# no missing

table(patdemsamp5_df$sex)

#       1       2   NA
# 6835722 8119629 1081 

table(patdemsamp5_df$rti_race)
  #     0        1        2        3        4        5        6     NA
  # 230516 11094526  1556068   124287   488226  1356882    64641  41286 

table(patdemsamp5_df$esrd_ind)

#        0        Y 
# 14813786   142646 
# no NA

table(is.na(patdemsamp5_df$death_dt))

  #  FALSE     TRUE 
  # 115669 14840763 

```


### Create dataset

```{r}
patdemsamp5_df <- read_rds("/project/Burke_PAC_MA/Analysis/Norman/Output/Rand Sample/patDemVar05p100224.rds")

mover_exp5 <- read_rds("/project/Burke_PAC_MA/Analysis/Norman/Output/Rand Sample/MovingAllQrt05p092724.rds")

mbsfcovFilt_df <- read_rds("/project/Burke_PAC_MA/Analysis/Norman/Output/Rand Sample/MBSFcov05p092824.rds")



cohraw_df <- read_rds('/project/Burke_PAC_MA/Analysis/Norman/Raw Data for R/SongCohortSel0618.rds')



hosp_jn <- cohraw_df %>%
  mutate(adm_date = dmy(admsndt), 
         hosp = 1) %>% 
   mutate(
    rfrnc_qrt = case_when(
      month(adm_date) %in% 1:3  ~ 1,
      month(adm_date) %in% 4:6  ~ 2,
      month(adm_date) %in% 7:9  ~ 3,
      month(adm_date) %in% 10:12 ~ 4),
    pac_ind = snf_flag ) %>% 
  select(bene_id, rfrnc_yr, rfrnc_qrt, hosp, fips_hosp, pac_ind) %>% 
  distinct()

table(hosp_jn$rfrnc_yr)

#    2015    2016    2017    2018    2019 
# 6355581 6075581 6250415 6202194 6191921 

table(hosp_jn$rfrnc_qrt)

#       1       2       3       4 
# 8504111 7607940 7371172 7592469 
```

```{r}
ddth_rm <- read_rds("/project/Burke_PAC_MA/Analysis/Norman/Output/Rand Sample/dthChkRmv092924.rds")

moverFinal_df <- mbsfcovFilt_df %>% # patient and coverage
  left_join(mover_exp5) %>% #mover info: join_by(bene_id)
  left_join(hosp_jn) %>% #hospitalization: join_by(bene_id, rfrnc_yr, rfrnc_qrt)
  left_join(patdemsamp5_df) %>% #patient demographics: join_by(bene_id, rfrnc_yr)
   anti_join(ddth_rm) # remove undead patient entries

  
 

moverFinal_df2 <- moverFinal_df %>%
  mutate(hosp_ind = ifelse(is.na(hosp) == TRUE, 0, 1 ),
         age = rfrnc_yr - year(dmy(bene_dob)),
         occ_fip = case_when(mover_ind == 0 ~ fip_strt,
                               mover_ind == 1 &
                                 (rfrnc_yr < move_yr |
                                    (rfrnc_yr == move_yr &
                                       rfrnc_qrt < move_qrt)) ~ fip_strt,
                               TRUE ~ fip_end),
         reference_date = case_when(
           rfrnc_qrt == 1 ~
             as.Date(paste( rfrnc_yr, "-01-01", sep = "")),
           rfrnc_qrt == 2 ~
             as.Date(paste(rfrnc_yr, "-04-01", sep = "")),
           rfrnc_qrt == 3 ~
             as.Date(paste(rfrnc_yr, "-07-01", sep = "")),
           rfrnc_qrt == 4 ~
             as.Date(paste(rfrnc_yr, "-10-01", sep = ""))),
         death_dt = dmy(death_dt)) %>%
  filter(death_dt >=  reference_date) %>%
  select(-hosp)

write_rds(moverFinal_df2, "/project/Burke_PAC_MA/Analysis/Norman/Output/Rand Sample/MoverCohPanel05p100224.rds")
```

#### Check

check var creation

```{r}
n_distinct(moverFinal_df2$bene_id)
#3607570




fav_stats(moverFinal_df2$age)
# min Q1 med Q3 max     mean       sd        n     missing
# 0   67  71 78 151  71.65817  11.32092  57475801   25795
 
moverFinal_df2 %>% filter(age < 60) %>% nrow()  
# 5742167, 0.099861 of dataset

table(moverFinal_df2$hosp_ind)
#        0        1 
# 55980203  1521413 
```
colSums(is.na(moverFinal_df2))

       bene_id       rfrnc_yr      rfrnc_qrt        FFS_ind 
             0              0              0              0 
        MA_ind       miss_ind         FM_ind      mover_ind 
             0              0              0              0 
     num_moves        move_yr       move_qrt       fip_strt 
             0       52122200       52122200              0 
       fip_end duplicate_flag           hosp      fips_hosp 
             0              0       55980183       56031888 
       pac_ind       esrd_ind       bene_dob            sex 
      55980183              0          25795           4130 
   rti_race_cd       death_dt       hosp_ind            age 
        149745       57220631              0          25795 
       occ_fip reference_date    pat_cnt_fip   hosp_cnt_fip 
             0              0              0              0 
       util_rt 
             0 

Check Deceased

```{r}
d_df <- moverFinal_df %>% 
  filter(is.na(bene_dob) == FALSE) %>% 
  group_by(bene_dob) %>% 
  filter(rfrnc_yr == max(rfrnc_yr, na.rm = TRUE) & 
           rfrnc_qrt == max(rfrnc_qrt, na.rm = TRUE))

#d_df$death_dt <- dmy(d_df$death_dt)

 d_df$reference_date = case_when(
       d_df$rfrnc_qrt == 1 ~ as.Date(paste( d_df$rfrnc_yr, "-01-01", sep = "")),
       d_df$rfrnc_qrt == 2 ~ as.Date(paste(d_df$rfrnc_yr, "-04-01", sep = "")),
       d_df$rfrnc_qrt == 3 ~ as.Date(paste(d_df$rfrnc_yr, "-07-01", sep = "")),
       d_df$rfrnc_qrt == 4 ~ as.Date(paste(d_df$rfrnc_yr, "-10-01", sep = ""))
    )
 
d_df$dth_chk = ifelse(d_df$death_dt <  d_df$reference_date, "Before", "After")
  # all should be after, 2 before

table(d_df$dth_chk)


# Gather rows with death mismatch
bene_rmv <- d_df %>% filter(dth_chk == "Before") %>% select(bene_id)

d_exp <- moverFinal_df 

 d_exp$reference_date = case_when(
       d_exp$rfrnc_qrt == 1 ~ as.Date(paste( d_exp$rfrnc_yr, "-01-01", sep = "")),
       d_exp$rfrnc_qrt == 2 ~ as.Date(paste(d_exp$rfrnc_yr, "-04-01", sep = "")),
       d_exp$rfrnc_qrt == 3 ~ as.Date(paste(d_exp$rfrnc_yr, "-07-01", sep = "")),
       d_exp$rfrnc_qrt == 4 ~ as.Date(paste(d_exp$rfrnc_yr, "-10-01", sep = ""))
    )
 d_exp2 <- d_exp %>% 
  inner_join(bene_rmv) %>% 
   filter(death_dt <  reference_date) %>%  # two patients removed
  select(bene_id, rfrnc_yr, rfrnc_qrt)

write_rds(d_exp2, "/project/Burke_PAC_MA/Analysis/Norman/Output/Rand Sample/dthChkRmv092924.rds")

# 2 patients died in 2015 and have entries afterward
    
```




```{r eval=FALSE, include=FALSE}
mbsfAll_df <- moverFinal_df %>%
  group_by(rfrnc_yr, bene_id) %>%
  summarise(hosp_yr = max(hosp_ind)) %>% 
  group_by(rfrnc_yr) %>% 
  summarise(hosp_cnt = sum(hosp_yr, na.rm = TRUE), pat_cnt = n()) %>% 
  mutate(hosp_perc = hosp_cnt/pat_cnt)


mbsf65pl_df <- moverFinal_df %>%
  filter(age > 65) %>% 
    group_by(rfrnc_yr, bene_id) %>%
  summarise(hosp_yr = max(hosp_ind)) %>% 
  group_by(rfrnc_yr) %>%
  summarise(hosp_cnt = sum(hosp_yr, na.rm = TRUE), pat_cnt = n()) %>% 
  mutate(hosp_perc = hosp_cnt/pat_cnt)

```





# Full County Data

### Prep raw mbsf

```{r}
mbsf_df <- fread("/project/Burke_PAC_MA/Analysis/Norman/Raw Data for R/RawMbsf1519.csv")

names(mbsf_df) <-tolower(names(mbsf_df))
```


```{r}
mbsf_exp <- mbsf_df %>% 
  mutate(fip_q1 = case_when(is.na(state_cnty_fips_cd_01) == FALSE ~ state_cnty_fips_cd_01,
                            is.na(state_cnty_fips_cd_01) == TRUE & 
                              is.na(state_cnty_fips_cd_02) == FALSE ~ state_cnty_fips_cd_02,
                            is.na(state_cnty_fips_cd_01) == TRUE & 
                              is.na(state_cnty_fips_cd_02) == TRUE & 
                              is.na(state_cnty_fips_cd_03) == FALSE ~ state_cnty_fips_cd_03, 
                            is.na(state_cnty_fips_cd_01) == TRUE & 
                              is.na(state_cnty_fips_cd_02) == TRUE & 
                              is.na(state_cnty_fips_cd_03) == TRUE ~ NA),
         fip_q2 = case_when(is.na(state_cnty_fips_cd_04) == FALSE ~ state_cnty_fips_cd_04,
                            is.na(state_cnty_fips_cd_04) == TRUE & 
                              is.na(state_cnty_fips_cd_05) == FALSE ~ state_cnty_fips_cd_05,
                            is.na(state_cnty_fips_cd_04) == TRUE & 
                              is.na(state_cnty_fips_cd_05) == TRUE & 
                              is.na(state_cnty_fips_cd_06) == FALSE ~ state_cnty_fips_cd_06, 
                            is.na(state_cnty_fips_cd_04) == TRUE & 
                              is.na(state_cnty_fips_cd_05) == TRUE & 
                              is.na(state_cnty_fips_cd_06) == TRUE ~ NA),
         fip_q3 = case_when(is.na(state_cnty_fips_cd_07) == FALSE ~ state_cnty_fips_cd_07,
                            is.na(state_cnty_fips_cd_07) == TRUE & 
                              is.na(state_cnty_fips_cd_08) == FALSE ~ state_cnty_fips_cd_08,
                            is.na(state_cnty_fips_cd_07) == TRUE & 
                              is.na(state_cnty_fips_cd_08) == TRUE & 
                              is.na(state_cnty_fips_cd_09) == FALSE ~ state_cnty_fips_cd_09, 
                            is.na(state_cnty_fips_cd_07) == TRUE & 
                              is.na(state_cnty_fips_cd_08) == TRUE & 
                              is.na(state_cnty_fips_cd_09) == TRUE ~ NA),
         fip_q4 = as.character(case_when(is.na(state_cnty_fips_cd_10) == FALSE ~ state_cnty_fips_cd_10,
                            is.na(state_cnty_fips_cd_10) == TRUE & 
                              is.na(state_cnty_fips_cd_11) == FALSE ~ state_cnty_fips_cd_11,
                            is.na(state_cnty_fips_cd_10) == TRUE & 
                              is.na(state_cnty_fips_cd_11) == TRUE & 
                              is.na(state_cnty_fips_cd_12) == FALSE ~ state_cnty_fips_cd_12, 
                            is.na(state_cnty_fips_cd_10) == TRUE & 
                              is.na(state_cnty_fips_cd_11) == TRUE & 
                              is.na(state_cnty_fips_cd_12) == TRUE ~ NA))) %>% 
  select(bene_id, rfrnc_yr, bene_dob, rti_race_cd, contains("fip_q"))

write_csv(mbsf_exp, "/project/Burke_PAC_MA/Analysis/Norman/SAS/MBSF2reshape.csv")

```


```{r}
#created in SAS QuartAgg_hospCoh
mbsfqrt_df <- fread("/project/Burke_PAC_MA/Analysis/Norman/Raw Data for R/mbsf_qrtCntyCnt.csv")
names(mbsfqrt_df) <-tolower(names(mbsfqrt_df))


cohraw_df <- fread("/project/Burke_PAC_MA/Analysis/Norman/Raw Data for R/SongCohort0618.csv")
names(cohraw_df) <-tolower(names(cohraw_df))

mover_expst5 <- readRDS("/project/Burke_PAC_MA/Analysis/Norman/Output/Rand Sample/MovingAllQrt05p140824.rds")

```


```{r}
hospqt_df <- cohraw_df %>% 
  mutate(rfrnc_qrt = quarter(dmy(admsndt)),
         occ_fip = fips_yr) %>% 
   group_by(occ_fip, rfrnc_yr, rfrnc_qrt) %>% 
  summarise(hosp_cnt = n())


Aggqt_df <- mbsfqrt_df %>%  
  mutate(occ_fip = as.numeric(occ_fip)) %>% 
  full_join(hospqt_df) %>% 
  mutate(hosp_cnt = ifelse(is.na(hosp_cnt) == TRUE, 0, hosp_cnt),
         util_rt = hosp_cnt /pat_uniq_count)

Aggqt_df
    
write_rds(Aggqt_df, "/project/Burke_PAC_MA/Analysis/Norman/Output/Rand Sample/mbsfHospQtAgg090324.rds")

mbsf_miss <- mbsfqrt_df %>% 
  filter(is.na(occ_fip) == TRUE | occ_fip < 10)
```

### Combine with sample
```{r}
Aggqt_df  <- read_rds("/project/Burke_PAC_MA/Analysis/Norman/Output/Rand Sample/mbsfHospQtAgg090324.rds")

panel_df <- readRDS("/project/Burke_PAC_MA/Analysis/Norman/Output/Rand Sample/MoverCohPanel05p092824.rds")

aggPanel_df <- panel_df %>% 
  left_join(Aggqt_df) %>% 
  rename(hosp_cnt_fip = hosp_cnt, 
         pat_cnt_fip = pat_uniq_count) %>% 
  arrange(bene_id, rfrnc_yr, rfrnc_qrt)
  

write_rds(aggPanel_df, "/project/Burke_PAC_MA/Analysis/Norman/Output/Rand Sample/PanelQtAgg092724.rds")

```

```{r}
table(is.na(aggPanel_df$util_rt)) # no NA
```

